### 2013-12-13 code/descriptive_analysis.Rmd
First pages commit

@@

```{ropts, echo=FALSE}
opts_chunk$set(echo=FALSE, dev='svg', eval=TRUE, cache=TRUE, fig.height=10, message=FALSE, warning=FALSE)
```

@@

```{rdescplot1_1, fig.width=15}
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
library(ggplot2)
library(reshape2)

>>>>

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

<link href="http://markuskainu.fi/material/css/rmarkdown.css" rel="stylesheet" type="text/css" title="compact"></link> <link href='http://fonts.googleapis.com/css?family=Oswald' rel='stylesheet' type='text/css'>

@@

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

```{rdescplot1_1, fig.width=15}
load("~/workspace/data/lits2.RData")
library(ggplot2)
library(reshape2)

### 2013-12-13 finalPlots.Rmd
First pages commit

# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpChange)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpChange) ~ COR, data=t4, mean),2)

@@

```{rattribFinalPlotsGini}
# UNU-Wider Gini

>>>>

# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe' & year == 2010)
west <- subset(macro, group_fine == 'West Europe' & year == 2010)
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpChange)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpChange) ~ COR, data=t4, mean),2)

@@

```{rattribFinalPlotsGini, eval=FALSE}
# UNU-Wider Gini
